A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-08-22 tex/paper.tex
ready for PH run

\begin{figure*}[!htb]
\begin{center}
  \includegraphics{correlation_panel.pdf}
  \caption{\textbf{Top}: A typical model fit to a data spectrum, with
  parameters drawn from the posterior distribution, and the residuals that
  result. \textbf{Left} The low-amplitude, mildly covariant residuals enlarged
  to show the mildly covariant structure produced by slight mismatch between
  the data and model spectra.   \textbf{Right} The autocorrelation of the
residual sequence shown at left. Notice that there is significant correlation
for offsets of $\lesssim 5$ pixels.}
\label{fig:class0}
\end{center}
\end{figure*}

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[draft,width=0.9\textwidth,height=4in]{figs/spectrum_region.pdf}
  \caption{The spectrum residuals and many random draws from the final covariance matrix showing how the uncertainty in the ``outlier'' lines is identified by the local covariance kernels. Plotted with the increased variance envelope over the residuals.
}
\label{fig:regions}
\end{center}
\end{figure*}

@@

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics{figs/badlines.pdf}
  \caption{A collection of spectral lines which have imperfect model fits.
    From left to right: \textbf{Class 0} The majority of spectral lines
    ($\gtrsim 60$\%) will have minor differences in strength between data and
    model spectrum, which produce low-amplitude correlations in the residuals
    on the length scale of the width of a typical spectral line.  \textbf{Class
    I}: Sometimes ($\lesssim 5$\% of all lines), a missing opacity source in
    the model (in this case a line-blended \ion{Ca}{2}) leaves a large, highly correlated
    patch of negative residuals.  \textbf{Class II}: Sometimes ($\lesssim 5$\%
    of all lines), an extraneous line in the model leaves a large, highly
    correlated patch of positive residuals.  \textbf{Class III}: If the line strengths are
    substantially discrepant ($\lesssim 10$\% of all lines), there will be many
    correlated residuals of moderate amplitude.  The difficulty
    with class III lines is that for any specific line, there might exist a
    $\vT$ that will fit the line, but there does not exist a $\vT$ that
    will properly fit \emph{all} the lines.}
\label{fig:badlines}
\end{center}
\end{figure*}

>>>>

\begin{figure}[!htb]
\begin{center}
  \includegraphics{residuals_23.pdf}
  \includegraphics{class0_residuals.pdf}
  \includegraphics{class0_autocorrelation.pdf}
  \caption{\textbf{Top}: A typical model fit to a data spectrum, with
  parameters drawn from the posterior distribution, and the residuals that
  result. \textbf{Left} The low-amplitude, mildly covariant residuals enlarged
  to show the mildly covariant structure produced by slight mismatch between
  the data and model spectra.   \textbf{Right} The autocorrelation of the
residual sequence shown at left. Notice that there is significant correlation
for offsets of $\lesssim 5$ pixels.}
\label{fig:class0}
\end{center}
\end{figure}

@@

@@

\begin{figure*}[!htb]
\begin{center}
  \includegraphics[draft,width=0.9\textwidth,height=3in]{figs/Gl51_residuals.pdf}
  \caption{The spectrum residuals and many random draws from the final covariance matrix showing how the uncertainty in the ``outlier'' lines is identified by the local covariance kernels. Plotted with the increased variance envelope over the residuals.}
\label{fig:regions}
\end{center}
\end{figure*}

\begin{figure}[!htb]
\begin{center}
  \includegraphics[draft,width=0.45\textwidth,height=3in]{figs/Gl51_posterior.pdf}
  \caption{The spectrum residuals and many random draws from the final covariance matrix showing how the uncertainty in the ``outlier'' lines is identified by the local covariance kernels. Plotted with the increased variance envelope over the residuals.}
\label{fig:gl_posterior}
\end{center}
\end{figure}

\begin{deluxetable}{lr@{$\pm$}l} 
\tablecaption{\label{table:PHOENIX}Gl51 {\sc Phoenix} results}
\tablehead{\colhead{Parameter} & \multicolumn{2}{c}{Value}}
\startdata
\cutinhead{Stellar parameters}
$T_{\rm eff}$ &  &  K \\
$\log_{10} g$ & \multicolumn{2}{c}{5.0 dex} \\
$\Z$ &  &  dex \\
$v \sin i$ &  &  $\kms$\\
$v_z$ &  &  $\kms$ \\
$\log_{10} \Omega$ &  & \\
\cutinhead{Nuisance parameters}
$\cc{22}{0}$ & & \\
$\cc{22}{1}$ & & \\
$\cc{22}{2}$ & & \\
$\cc{22}{3}$ & & \\
$b$ & & \\
$a_{\rm g} $ & & \\
$l$ & & \\
\cutinhead{Local kernel parameters}
& & \\
& & \\
& & \\
\hline\\
& & \\
& & \\
& & \\
\hline\\
& & \\
& & \\
& & \\
\enddata
\end{deluxetable}

@@

\begin{figure}[!htb]
\begin{center}
  \includegraphics{figs/badlines0.pdf}
  \includegraphics{figs/badlines1.pdf}
  \includegraphics{figs/badlines2.pdf}
  \includegraphics{figs/badlines3.pdf}
  \caption{A collection of spectral lines which have imperfect model fits.
    \textbf{First panel} The majority of spectral lines ($\gtrsim 60$\%) will
    have minor differences in strength between data and model spectrum, which
    produce low-amplitude correlations in the residuals on the length scale of
    the width of a typical spectral line.  \textbf{Second panel}: Sometimes
    ($\lesssim 5$\% of all lines), a missing opacity source in the model (in
    this case a line-blended \ion{Ca}{2}) leaves a large, highly correlated
    patch of negative residuals.  \textbf{Third panel}: Sometimes ($\lesssim
    5$\% of all lines), an extraneous line in the model leaves a large, highly
    correlated patch of positive residuals. \textbf{Fourth panel}: If the line
    strengths are substantially discrepant ($\lesssim 10$\% of all lines),
    there will be many correlated residuals of moderate amplitude.  The
    difficulty with class III lines is that for any specific line, there might
    exist a $\vT$ that will fit the line, but there does not exist a $\vT$ that
    will properly fit \emph{all} the lines.}
\label{fig:badlines}
\end{center}
\end{figure}
